---
title: "Variable tables"
format:
  pdf:
    documentclass: article
    classoption: [landscape]
    geometry:
      - top=20mm
      - bottom=20mm 
      - left=20mm
      - right=20mm    
editor: visual

---

```{r, echo=FALSE, message=FALSE, warning=FALSE}

library(tidyverse)
library(kableExtra)
library(flextable)

```

```{r,  echo=FALSE}

surv1 <- read.csv("variables/survey1.csv")
colnames(surv1) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

surv2 <- read.csv("variables/survey1.csv")
colnames(surv2) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

ath <- read.csv("variables/atheism.csv")
colnames(ath) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

big <- read.csv("variables/belief in god.csv")
colnames(big) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

rel <- read.csv("variables/religiosity.csv")
colnames(rel) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

meta <- read.csv("variables/meta-belief.csv")
colnames(meta) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

snb <- read.csv("variables/supernatural-belief.csv")
colnames(snb) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

dem <- read.csv("variables/demographics.csv", header = TRUE)
colnames(dem) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")
  

agreement <- read.csv("variables/agreement.csv", header = TRUE)
colnames(agreement) <- c("Strongly Disagree", "Moderately Disagree", "Slightly Disagree", "Neither Agree nor Disagree", "Slightly Agree", "Moderately Agree", "Strongly Agree")

```

## Survey 1

```{r, echo=FALSE, warning=FALSE}

#table is too long so we split it

# tab 1

surv1.1 <- surv1[1:13,]

 kbl(surv1.1,
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:13), hline_after = T)
 

```
\newpage
```{r, echo=FALSE, warning=FALSE}

# tab 2

surv1.2 <- surv1[13:26,]
rownames(surv1.2) <- NULL


kbl(surv1.2,
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:13), hline_after = T)


```

## Belief Measures

### Belief in God

```{r, echo=FALSE}

big1 <- big[1:4,]

rownames(big1) <- NULL

kbl(big1,
    "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:4), hline_after = T)
```

\newpage

```{r, echo=FALSE}

big2 <- big[5:6,]

rownames(big2) <- NULL

kbl(big2, 
    "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:4), hline_after = T)
```

\newpage

### Atheism

```{r, echo=FALSE}
kbl(ath, 
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:4), hline_after = T)
```

### Religiosity

```{r, echo=FALSE}
rel1 <- rel[1:6,]
rownames(rel1) <- NULL

kbl(rel1,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)
```

```{r, echo=FALSE}
rel2 <- rel[7:10,]
rownames(rel2) <- NULL

kbl(rel2,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:3), hline_after = T)
```


### Meta-Belief

```{r, echo=FALSE}
kbl(meta,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:7), hline_after = T)
```

\newpage

### Supernatural Belief

Supernatural Belief measures use a 1-7 agreement scale

*Afterlife*\

```{r, echo=FALSE, warning=FALSE}

#table is too long so we split it

snb1 <- snb[1:3,]

rownames(snb1) <- NULL



kbl(snb1,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)


```

\

*Reincarnation*\

```{r, echo=FALSE, warning=FALSE}


#table is too long so we split it

snb2 <- snb[4,]
rownames(snb2) <- NULL


kbl(snb2,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)


```

\newpage

*Astrology*\

```{r, echo=FALSE, warning=FALSE}


#table is too long so we split it

snb3 <- snb[5,]

rownames(snb3) <- NULL



kbl(snb3,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)


```

\

*Mystical Powers*\

```{r, echo=FALSE, warning=FALSE}


#table is too long so we split it

snb4 <- snb[6:7,]
rownames(snb4) <- NULL



kbl(snb4,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)

```

\newpage

*Underlying Forces*\

```{r, echo=FALSE, warning=FALSE}


#table is too long so we split it

snb5 <- snb[8:11,]
rownames(snb5) <- NULL



kbl(snb5,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)


```

\newpage

*Supernatural Beings*\

```{r, echo=FALSE, warning=FALSE}


#table is too long so we split it

snb6 <- snb[12:14,]
rownames(snb6) <- NULL



kbl(snb6,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)


```

\

*Evil Eye*\

```{r, echo=FALSE, warning=FALSE}


#table is too long so we split it

snb7 <- snb[15,]
rownames(snb7) <- NULL



kbl(snb7,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)


```

\newpage

*Spiritual Experience*\

```{r, echo=FALSE, warning=FALSE}


#table is too long so we split it

snb8 <- snb[16,]
rownames(snb8) <- NULL



kbl(snb8,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)

```

\

*Lucky Objects*\

```{r, echo=FALSE, warning=FALSE}


#table is too long so we split it

snb9 <- snb[17,]
rownames(snb9) <- NULL



kbl(snb9,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)


```
\newpage

#### Demographic Variables

```{r, echo=FALSE, warning=FALSE}

rownames(dem) <- NULL



kbl(dem,  
     "latex",
     booktabs = T) %>%
              kable_styling(full_width = T,
                            fixed_thead = T,
                            latex_options = c("scale_down")) %>%
              column_spec(1, width = "3cm") %>%
              column_spec(2, width = "4cm") %>%
              column_spec(3, width = "4cm") %>%
              column_spec(4, width = "3cm") %>%
              column_spec(5, width = "3cm") %>%
              column_spec(6, width = "4cm") %>%
              row_spec(0, hline_after = T, bold = TRUE)  %>%
              row_spec(c(1:10), hline_after = T)


```
