---
title: "Tolerance of Ambiguity"
author: "Connair J. S. Russell"
bibliography: lib.bib
csl: apa.csl
number-depth: 2
---

```{r, echo=FALSE, message=FALSE}

# echo and message false so not shown on page

library(dplyr)
library(kableExtra)

cogstyles <- read.csv("variables/survey2.csv")
colnames(cogstyles) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")

tatab <- cogstyles %>%filter(`Variable Name`=="Tolerance of Ambiguity")

```

**Cluster:** Cognitive Styles

## Measure

The measure used for tolerance of ambiguity is the Multiple Stimulus Types Ambiguity Tolerance Scale- II (MSTAT-II) by @mclain2009 .

### Modifications {.unnumbered}

## Implementation

### Question wording {.unnumbered}

Participants read the following text:

*Please read each of the following statements carefully and state to what extent you agree with each. There are no right or wrong answers and your responses remain anonymous.*

### Items {.unnumbered}

| Qlabel | question                                                                                       |
|-------------|-----------------------------------------------------------|
| at_01  | I don't tolerate ambiguous situations well                                                     |
| at_02  | I would rather avoid solving a problem that must be viewed from several different perspectives |
| at_03  | I try to avoid situations that are ambiguous                                                   |
| at_04  | I prefer familiar situations to new ones                                                       |
| at_05  | Problems that cannot be considered from just one point of view are a little threatening        |
| at_06  | I avoid situations that are too complicated for me to easily understand                        |
| at_07  | I am tolerant of ambiguous situations                                                          |
| at_08  | I enjoy tackling problems that are complex enough to be ambiguous                              |
| at_09  | I try to avoid problems that don't seem to have only one "best" solution                       |
| at_10  | I generally prefer novelty over familiarity                                                    |
| at_11  | I dislike ambiguous situations                                                                 |
| at_12  | I find it hard to make a choice when the outcome is uncertain                                  |
| at_13  | I prefer a situation in which there is some ambiguity                                          |

### Coding {.unnumbered}

This questionnaire uses our standard response scale for agreement,

| **1**             | **2**               | **3**             | **4**                      | **5**          | **6**            | **7**          |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| strongly disagree | moderately disagree | slightly disagree | neither agree nor disagree | slightly agree | moderately agree | strongly agree |

`at_01, at_02, at_03, at_04, at_05, at_06, at_09, at_11, and at_12 are reverse coded`

### Scoring

The following variables are derived from this measure:

```{r, echo=FALSE}
kbl(tatab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 
```

