---
title: "Anthropomorphism"
author: "Connair J. S. Russell"
bibliography: lib.bib
csl: apa.csl
number-depth: 2
---

```{r, echo=FALSE, message=FALSE}

library(dplyr)
library(kableExtra)
library(flextable)

cogbi <- read.csv("variables/survey2.csv")
colnames(cogbi) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")

tab <- cogbi %>%filter(`Variable Name`=="Anthropomorphism")

```

## Measure

### Modifications {.unnumbered}

The original measure used by @neave2015 questions pertaining to childhood and adulthood experiences. For the sake of brevity only questions pertaining to adulthood were included.

For consistency with the other agreement based measures used in the project the anchors and response items were altered to be a 7-point Likert scale.

## Implementation

### Question wording {.unnumbered}

Participants read the following text:

*Please read each of the following statements carefully and rate how strongly you agree or disagree. There are no right or wrong answers and your responses remain anonymous.*

### Items {.unnumbered}

| Qlabel  | question                                                                                                                            |
|------------|------------------------------------------------------------|
| anth_01 | I sometimes wonder if my computer deliberately runs more slowly after I have shouted at it                                          |
| anth_02 | On occasions I feel that my computer/printer is being deliberately awkward                                                          |
| anth_03 | I sometimes wonder if my personal possessions appreciate it when I have given them a good clean                                     |
| anth_04 | On occasion I feel that the weather conditions are being deliberately bad in order to ruin a social event                           |
| anth_05 | I do think that certain cars have a specific personality                                                                            |
| anth_06 | If I accidentally break one of my favourite possessions I make sure that I apologise to it for my clumsiness                        |
| anth_07 | I think that some trees are friendly while others have an air of menace                                                             |
| anth_08 | I sometimes think that if my computer/printer is made to feel happy and/or wanted, then they will be less likely to malfunction     |
| anth_09 | I sometimes feel that the sea can be angry                                                                                          |
| anth_10 | Part of the reason why I picked a new car/electrical item was because when I first saw it I felt that it had a friendly personality |

### Coding {.unnumbered}

This questionnaire follows our standard coding for agreement based measures, with strongly disagree = 1, and strongly agree = 7.

|                   |                     |                   |                            |                |                  |                |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| **1**             | **2**               | **3**             | **4**                      | **5**          | **6**            | **7**          |
| strongly disagree | moderately disagree | slightly disagree | neither agree nor disagree | slightly agree | moderately agree | strongly agree |

`No items are reverse coded`

### Scoring

The following variables were derived from this measure

```{r, echo=FALSE}
if (knitr::pandoc_to("html")) {
kbl(tab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 

} else {
  # do use gt
tab %>%
  flextable() %>%
  width(j = 1, width = 3, unit = "cm") %>%
  width(j = 2, width = 3, unit = "cm") %>%
  width(j = 3, width = 3, unit = "cm") %>%
  width(j = 4, width = 3, unit = "cm") %>%
  width(j = 5, width = 3, unit = "cm") %>%
  width(j = 6, width = 3, unit = "cm") %>%
  theme_vanilla()
}
   
```
