# Belief Measures {.unnumbered}

The variables defined here are derived from the following measures for which detailed information can be found on their respective pages:

-   [ISSP](issp.qmd)
-   [Religious Identity](religiousidentity.qmd)
-   [Religious Practice](religiouspractice.qmd)
-   [Supernatural Belief](supernaturalbelief.qmd)
-   [General Belief](generalbelief.qmd)
-   [Atheist Membership](atheistmembership.qmd)


## Belief Variables

```{r, echo=FALSE, message=FALSE}

library(dplyr)
library(kableExtra)



ath <- read.csv("variables/atheism.csv")
colnames(ath) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

big <- read.csv("variables/belief in god.csv")
colnames(big) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

rel <- read.csv("variables/religiosity.csv")
colnames(rel) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

meta <- read.csv("variables/meta-belief.csv")
colnames(meta) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

snb <- read.csv("variables/supernatural-belief.csv")
colnames(snb) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Definition", "Response Options")

  

agreement <- read.csv("variables/agreement.csv", header = TRUE)
colnames(agreement) <- c("Strongly Disagree", "Moderately Disagree", "Slightly Disagree", "Neither Agree nor Disagree", "Slightly Agree", "Moderately Agree", "Strongly Agree")
```


### Belief in God

```{r, echo=FALSE}
kbl(big, booktabs = T) %>%
  kable_styling(full_width = T)%>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "3cm") %>%
  column_spec(4, width = "3cm") %>%
  column_spec(5, width = "3cm") %>%
  column_spec(6, width = "3cm")
```

### Religiosity

```{r, echo=FALSE}
kbl(rel, booktabs = T) %>%
  kable_styling(full_width = T)%>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "3cm") %>%
  column_spec(4, width = "3cm") %>%
  column_spec(5, width = "3cm") %>%
  column_spec(6, width = "3cm") 
```

### Atheism

```{r, echo=FALSE}
kbl(ath, booktabs = T) %>%
  kable_styling(full_width = T)%>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "3cm") %>%
  column_spec(4, width = "3cm") %>%
  column_spec(5, width = "3cm") %>%
  column_spec(6, width = "3cm")
```

### Meta-Belief

```{r, echo=FALSE}
kbl(meta, booktabs = T) %>%
  kable_styling(full_width = T)%>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "3cm") %>%
  column_spec(4, width = "3cm") %>%
  column_spec(5, width = "3cm") %>%
  column_spec(6, width = "3cm") 
```

### Supernatural Belief

Supernatural Belief measures use our 1-7 agreement scale:

```{r, echo=FALSE, warning=FALSE}
kbl(agreement,
    booktabs = T,
    align = "c") %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "2.5cm") %>%
             column_spec(2, width = "2.5cm") %>%
             column_spec(3, width = "2.5cm") %>%
             column_spec(4, width = "2.5cm") %>%
             column_spec(5, width = "2.5cm") %>%
             column_spec(6, width = "2.5cm") %>%
             column_spec(7, width = "2.5cm") 

```

#### Supernatural Belief Variables

```{r, echo=FALSE, warning=FALSE}

rownames(snb) <- NULL



kbl(snb,
    booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm")


```
