---
title: "Dualism"
author: "Connair J. S. Russell"
number-depth: 2
---

```{r, echo=FALSE, message=FALSE, eval=FALSE}

# echo and message false so not shown on page

library(dplyr)
library(kableExtra)

cogbi <- read.csv("variables/cog-bias.csv")
colnames(cogbi) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")

duatab <- cogbi %>% filter(`Variable Name`=="Dualism")

```

**Cluster:** Cognitive Biases

## Measure

The Dualism measure used is an abbreviation of The Dualism Scale by @stanovich1989. As with previous research the scale has been shortened for brevity [@willard2017; @willard2020].

### Modifications.

For consistency with the other agreement based measures used in the project the anchors and response items were altered to be a 7-point Likert scale

## Implementation

### Question wording

Participants read the following text, adapted and shortened from @stanovich1989:

*Please read each of the following statements carefully and rate how strongly you agree or disagree. There are no right or wrong answers and your responses remain anonymous*

### Items {.unnumbered}

| Qlabel | question                                                                                                                                 |
|--------|------------------------------------------------------------------------------------------------------------------------------------------|
| dua_01 | The mind is not part of the brain but it affects the brain.                                                                              |
| dua_02 | When I imagine a scene in my mind, I am in a state that will forever be beyond explanation by science.                                   |
| dua_03 | The mind is a special form of energy (currently unknown to man) that is in contact with the brain and affects it.                        |
| dua_04 | When people talk about their minds they are really just talking about what their brains seem to be doing.                                |
| dua_05 | The fact that I can know my own thought processes (that I can introspect) means that my thought processes cannot be just brain processes |
| dua_06 | The mind is a nonmaterial substance that interact with the brain to determine behavior                                                   |
| dua_07 | Minds are inside brains but are not the same as brains.                                                                                  |
| dua_08 | Some mental processes have no connection to brain processes                                                                              |
| dua_09 | Mental processes are the result of activity in the nervous system                                                                        |
| dua_10 | The mind and the brain are two totally separate things                                                                                   |

### Coding {.unnumbered}

This questionnaire follows our standard scoring for agreement based measures, with strongly disagree = 1, and strongly agree = 7.

|                   |                     |                   |                            |                |                  |                |
|-------------------|---------------------|-------------------|----------------------------|----------------|------------------|----------------|
| **1**             | **2**               | **3**             | **4**                      | **5**          | **6**            | **7**          |
| strongly disagree | moderately disagree | slightly disagree | neither agree nor disagree | slightly agree | moderately agree | strongly agree |

`dua_04 and dua_09 are reverse coded`


## Scoring

```{r, echo=FALSE, message=FALSE, eval=FALSE}

kbl(duatab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 
```

## Script

```{r, eval = FALSE}
```

