---
title: "Existential Insecurity"
author: "Connair J. S. Russell"
number-depth: 2
---

```{r, echo=FALSE, message=FALSE}

# echo and message false so not shown on page

library(dplyr)
library(kableExtra)
library(flextable)

mot <- read.csv("variables/survey2.csv")
colnames(mot) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")

tab <- mot %>%  filter(`Variable Name`%in% c("Social Trust", "Wealth Inequality", "Social Security") | grepl("^Existential", `Variable Name`) )

```

**Cluster:** Motivational

## Measure

The initial existential insecurity measures were derived from those used by @baimel2022 and by @willard2017.

### Modifications {.unnumbered}

The food security measure from @baimel2022 was combined with financial and physical security from @willard2017, these were asked for 'recently' and 'for the forthcoming months'. 

In this wave we only included questions pertaining to childhood.

## Implementation

### Question wording {.unnumbered}

The question wording was as follows:

| Questions     | Question Text                                                |
|-----------------|-------------------------------------------------------|
| es_15 - es_21 | *When growing up did you:*                                   |


### Items {.unnumbered}

The question items were as follows:

**Existential Security**

| Qlabel | question                                                                       |
|-------------|-----------------------------------------------------------|
| es_15 | worry that your household may not able to buy or produce enough food to eat? |
| es_16 | feel that your household may not be able to afford to buy items you need     |
| es_17 | worry that your household may not have enough money                          |
| es_18 | worry about members of your household losing their job                       |
| es_19 | feel you will be safe walking alone in your local area after dark            |
| es_20 | worry about being burgled                                                    |
| es_21 | worry about being a victim of violent crime                                  |


### Coding {.unnumbered}

Items on the existential security subscale use the following frequency based Likert scale:

|       |                   |              |           |            |                 |        |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| **1** | **2**             | **3**        | **4**     | **5**      | **6**           | **7**  |
| never | very infrequently | infrequently | sometimes | frequently | very frequently | always |


`es_19 is reverse coded`

### Scoring

The following variables are derived form this measure:

```{r, echo=FALSE, message=FALSE}

if (knitr::pandoc_to("html")) {
kbl(tab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 

} else {
  # do use gt
tab %>%
  flextable() %>%
  width(j = 1, width = 3, unit = "cm") %>%
  width(j = 2, width = 3, unit = "cm") %>%
  width(j = 3, width = 3, unit = "cm") %>%
  width(j = 4, width = 3, unit = "cm") %>%
  width(j = 5, width = 3, unit = "cm") %>%
  width(j = 6, width = 3, unit = "cm") %>%
  theme_vanilla()
}

```


