---
title: "Importance of Rationality"
author: "Connair J. S. Russell"
number-depth: 2
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}

library(tidyverse)
library(kableExtra)
library(flextable)

cogstyles <- read.csv("variables/survey2.csv")
colnames(cogstyles) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")


tab <- cogstyles %>% filter(`Variable Name` == "Importance of Rationality")

```

**Cluster:** Cognitive Style

## Measure

Here we include the Importance of Rationality Scale from @stahl2016

### Modifications {.unnumbered}

## Implementation

### Question wording {.unnumbered}

Participants read the following text:

*Please read each of the following statements carefully and state to what extent you agree. There are no right or wrong answers and your responses remain anonymous.*

**INSERT**

### Items {.unnumbered}

|        |                                                                                                       |
|-----------------------|-------------------------------------------------|
| imp_01 | It is important to me personally to be skeptical about claims that are not backed up by evidence.     |
| imp_02 | It is important to me personally to remain rational and levelheaded even in heated arguments.         |
| imp_03 | It is important to me personally to examine traditionally held beliefs using logic and evidence.      |
| imp_04 | It is important to me personally that I can justify my beliefs using rational arguments and evidence. |
| imp_05 | It is important to me personally to critically examine my long-held beliefs.                          |
| imp_06 | It is important to me personally to be a rational person.                                             |

### Coding {.unnumbered}

This questionnaire uses our standard agreement scale.

| **1**             | **2**               | **3**             | **4**                      | **5**          | **6**            | **7**          |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| strongly disagree | moderately disagree | slightly disagree | neither agree nor disagree | slightly agree | moderately agree | strongly agree |

`No items are reverse coded`

### Scoring {.unnumbered}

The following variables are derived form this measure:

```{r, echo=FALSE, eval=TRUE}
if (knitr::pandoc_to("html")) {
kbl(tab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 

} else {
tab %>%
  flextable() %>%
  width(j = 1, width = 3, unit = "cm") %>%
  width(j = 2, width = 3, unit = "cm") %>%
  width(j = 3, width = 3, unit = "cm") %>%
  width(j = 4, width = 3, unit = "cm") %>%
  width(j = 5, width = 3, unit = "cm") %>%
  width(j = 6, width = 3, unit = "cm") %>%
  theme_vanilla()
}
```




