---
title: "Meaning in Life"
author: "Connair J. S. Russell"
number-depth: 2
---

```{r, echo=FALSE, message=FALSE, eval= TRUE}

library(tidyverse)
library(kableExtra)
library(flextable)

mot <- read.csv("variables/survey1.csv")
colnames(mot) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")


tab <- mot %>% filter(startsWith(`Variable Name`, "Meaning in Life"))


```

**Cluster:** Motivational

## Measure

To examine need for meaning we used The Meaning in Life Questionnaire (MLQ) by @steger2006. THe original scale has a two factor structure, with the subscales noted below. 

### Modifications {.unnumbered}

The truth-based Likert scale in the MLQ is the standard 7-point truth scale we used throughout the project so this was not altered.

We used the original question wording for the MLQ.

## Implementation

### Question wording {.unnumbered}

Participants read the following text:

*Please read each of the following statements carefully and rate how strongly you agree or disagree. There are no right or wrong answers and your responses remain anonymous.*

### Items

**Meaning in Life Questionnaire**

| Qlabel | Subscale | question                                                                 |
|--------------|--------------|--------------------------------------------|
| mlq_01 | presence | I understand my life's meaning.                                          |
| mlq_02 | search   | I am looking for something that makes my life feel meaningful.           |
| mlq_03 | search   | I am always looking to find my life's purpose.                           |
| mlq_04 | presence | My life has a clear sense of purpose                                     |
| mlq_05 | presence | I have a good sense of what makes my life meaningful.                    |
| mlq_06 | presence | I have discovered a satisfying life purpose.                             |
| mlq_07 | search   | I am always searching for something that makes my life feel significant. |
| mlq_08 | search   | I am seeking a purpose or mission for my life.                           |
| mlq_09 | presence | My life has no clear purpose.                                            |
| mlq_10 | search   | I am searching for meaning in my life.                                   |



## Coding

**The Meaning in Life Questionnaire (mlq\_ items) used our standard response scale for truth:**

|                   |               |                 |                         |               |             |                 |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| **1**             | **2**         | **3**           | **4**                   | **5**         | **6**       | **7**           |
| absolutely untrue | mostly untrue | somewhat untrue | can't say true or false | somewhat true | mostly true | absolutely true |

`Item mlq_09 is reverse coded`

## Scoring

```{r, echo=FALSE, message=FALSE, eval= TRUE}
if (knitr::pandoc_to("html")) {
kbl(tab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 

} else {
tab %>%
  flextable() %>%
  width(j = 1, width = 3, unit = "cm") %>%
  width(j = 2, width = 3, unit = "cm") %>%
  width(j = 3, width = 3, unit = "cm") %>%
  width(j = 4, width = 3, unit = "cm") %>%
  width(j = 5, width = 3, unit = "cm") %>%
  width(j = 6, width = 3, unit = "cm") %>%
  theme_vanilla()
}
```

