---
title: "Mentalizing"
author: "Connair J. S. Russell"
number-depth: 2
---

```{r, echo=FALSE, message=FALSE, eval= TRUE}

library(dplyr)
library(kableExtra)
library(flextable)

cogbi <- read.csv("variables/survey2.csv")
colnames(cogbi) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")

tab <- cogbi %>%filter(`Variable Name`=="Mentalizing")

```

**Cluster:** Cognitive Biases

## Measure

The Mentalizing measure used was the EQ-Short [@wakabayashi2006], which is an abbreviated version of the original Empathy Quotient measure [@baron-cohen2004].

### Modifications

In contrast with other agreement based measures we used, the selected mentalizing measure used a unique scoring system, and as such was not altered to be consistent with our other Likert measures.

The wording of the question was altered to reflect the manner of administration ("select" your answer instead of the original "circle")

## Implementation

### Question wording {.unnumbered}

Participants read the following text:

*Please read each of the following statements carefully and rate how strongly you agree or disagree. There are no right or wrong answers and your responses remain anonymous.*

### Items {.unnumbered}

| Qlabel | question                                                                                                |
|--------|---------------------------------------------------------------------------------------------------------|
| mnt_01 | I can easily tell if someone else wants to enter a conversation.                                        |
| mnt_02 | I really enjoy caring for other people                                                                  |
| mnt_03 | I find it hard to know what to do in a social situation                                                 |
| mnt_04 | I often find it difficult to judge if something is rude or polite                                       |
| mnt_05 | In a conversation, I tend to focus on my own thoughts rather than on what my listener might be thinking |
| mnt_06 | I can pick up quickly if someone says one thing but means another.                                      |
| mnt_07 | It is hard for me to see why some things upset people so much                                           |
| mnt_08 | I find it easy to put myself in somebody else's shoes                                                   |
| mnt_09 | I am good at predicting how someone will feel.                                                          |
| mnt_10 | I am quick to spot when someone in a group is feeling awkward or uncomfortable                          |
| mnt_11 | I can't always see why someone should have felt offended by a remark                                    |
| mnt_12 | I don't tend to find social situations confusing.                                                       |
| mnt_13 | Other people tell me I am good at understanding how they are feeling and what they are thinking         |
| mnt_14 | I can easily tell if someone else is interested or bored with what I am saying                          |
| mnt_15 | Friends usually talk to me about their problems as they say that I am very understanding.               |
| mnt_16 | I can sense if I am intruding, even if the other person doesn't tell me                                 |
| mnt_17 | Other people often say that I am insensitive, though I don't always see why                             |
| mnt_18 | I can tune into how someone else feels rapidly and intuitively.                                         |
| mnt_19 | I can easily work out what another person might want to talk about                                      |
| mnt_20 | I can tell if someone is masking their true emotion                                                     |
| mnt_21 | I am good at predicting what someone will do                                                            |
| mnt_22 | I tend to get emotionally involved with a friend's problems                                             |

### Coding {.unnumbered}

The mentalizing measure follows a bespoke 4 point agreement scale and uses a the following coding scheme:

| definitely disagree | slightly disagree | slightly agree | definitely agree |
|---------------------|-------------------|----------------|------------------|
| 0                   | 0                 | 1              | 2                |

`Items 03, 04, 05, 07, 11, and 17 are reverse coded.`

### Scoring

The following variables are derived from this measure:

```{r, echo=FALSE, message=FALSE, eval= TRUE}
if (knitr::pandoc_to("html")) {
kbl(tab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 

} else {
tab %>%
  flextable() %>%
  width(j = 1, width = 3, unit = "cm") %>%
  width(j = 2, width = 3, unit = "cm") %>%
  width(j = 3, width = 3, unit = "cm") %>%
  width(j = 4, width = 3, unit = "cm") %>%
  width(j = 5, width = 3, unit = "cm") %>%
  width(j = 6, width = 3, unit = "cm") %>%
  theme_vanilla()
}
   
```

