---
title: "Promiscuous Teleology"
author: "Connair J. S. Russell"
number-depth: 2
---

```{r, echo=FALSE, message=FALSE, eval=TRUE}

library(dplyr)
library(kableExtra)
library(flextable)

cogbi <- read.csv("variables/survey2.csv")
colnames(cogbi) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")

tab <- cogbi %>%filter(`Variable Name`=="Promiscuous Teleology")

```

## Measure

The promiscuous teleology measure we use is the short form of the Teleological Ideas about Nature Scale (TINS), which is an as yet unpublished scale by Kelemen, Brown, Burnham & Rottman (2023, in prep).

`PAGE WILL BE UPDATED WHEN THE SCALE IS PUBLISHED`


### Modifications {.unnumbered}

## Implementation

### Question wording {.unnumbered}

Participants read the following text:

*Please read each of the following statements carefully and state to what extent you agree. There are no right or wrong answers and your responses remain anonymous.*

### Items {.unnumbered}


### Coding {.unnumbered}

This questionnaire used the standard response scale for agreement

`No items are reverse coded`

### Scoring

The following variables are derived from this measure:

```{r, echo=FALSE, eval=TRUE}
if (knitr::pandoc_to("html")) {
kbl(tab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 

} else {
tab %>%
  flextable() %>%
  width(j = 1, width = 3, unit = "cm") %>%
  width(j = 2, width = 3, unit = "cm") %>%
  width(j = 3, width = 3, unit = "cm") %>%
  width(j = 4, width = 3, unit = "cm") %>%
  width(j = 5, width = 3, unit = "cm") %>%
  width(j = 6, width = 3, unit = "cm") %>%
  theme_vanilla()
}
   
```

## Script


```{r, eval = FALSE}


```

