---
title: "Rebelliousness"
author: "Connair J. S. Russell"
number-depth: 2
---

```{r, echo=FALSE, message=FALSE, eval= FALSE}

library(dplyr)
library(kableExtra)

morvals <- read.csv("variables/morals-vals.csv")
colnames(morvals) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")

rebtab <- morvals %>% filter(grepl("^Rebelliousness",`Variable Name`))

```

**Cluster:** Morals/Values

## Measure

The rebelliousness measure is a custom measure devised to examine the subscales pro-active rebelliousness and reactive rebelliousness identified by @mcdermott2001. After wave 1 we exluded what we termed the "Activism" subscale and only included the "Trolling" subscale in this round.

### Modifications {.unnumbered}

## Implementation

### Question wording {.unnumbered}

Participants read the following text:

*Please read each of the following statements carefully and state to what extent they apply to you. There are no right or wrong answers and your responses remain anonymous.*

### Items {.unnumbered}

| Qlabel | **Subscale** | question                                                              |
|-----------------|-----------------|---------------------------------------|
| reb_01 | Trolling     | I find it exciting to poke fun at people                              |
| reb_02 | Trolling     | I find it exciting to poke fun at authority                           |
| reb_03 | Trolling     | I experience a thrill when disobeying authority                       |
| reb_04 | Trolling     | I experience an urge to disobey social rules                          |

### Coding {.unnumbered}

This questionnaire follows our standard coding for extent based measures, with To No Extent At All = 1, and To a Great Extent = 7.

| **1**               | **2**              | **3**            | **4**                | **5**                    | **6**                    | **7**             |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| To No Extent At All | To a Slight Extent | To a Mild Extent | To a Moderate Extent | To an Appreciable Extent | To a Considerable Extent | To a Great Extent |

`No items are reverse coded`

### Scoring

The following variables are derived from this measure.

```{r, echo=FALSE, eval= FALSE}
kbl(rebtab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 
```

