---
title: "Thinking Style"
author: "Connair J. S. Russell"
number-depth: 2
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

library(tidyverse)
library(kableExtra)

cogstyles <- read.csv("variables/cog-styles.csv")
colnames(cogstyles) <- c("Variable Name", "Variable Label", "Description", "Variable Type", "Source (Section)", "Definition")

tstab <- cogstyles %>% filter(grepl("^Cognitive Style", `Variable Name`))

```

**Cluster:** Cognitive Style

## Measure

We use the original Cognitive Reflection Task by @frederick2005, and an updated version, the Cognitive Reflection Task 2,from @thomson2016.

### Modifications {.unnumbered}

## Implementation

### Question wording {.unnumbered}

Participants read the following text:

*In the following section you will be asked a series of questions. Please do your best to answer as accurately as possible.*

### Items {.unnumbered}

| Qlabel | question                                                                                                                                                                                                    |
|---------------------|---------------------------------------------------|
| crt_01 | You're running a race and you pass the person in second place, what place are you in?                                                                                                                       |
| crt_02 | A farmer had 15 sheep and all but 8 died. How many are left?                                                                                                                                                |
| crt_03 | Emily's father has three daughters. The first two are named April and May. What is the third daughter's name?                                                                                               |
| crt_04 | How many cubic feet of dirt are there in a hole that is 3' deep x 3' wide x 3' long?                                                                                                                        |
| crt_05 | A bat and a ball cost \$1.10 in total. The bat costs \$1.00 more than the ball. How much does the ball cost?                                                                                                |
| crt_06 | If it takes 5 machines 5 min to make 5 widgets, how long would it take 100 machines to make 100 widgets?                                                                                                    |
| crt_07 | In a lake, there is a patch of lily pads. Every day, the patch doubles in size. If it takes 48 days for the patch to cover the entire lake, how long would it take for the patch to cover half of the lake? |

### Coding {.unnumbered}

This questionnaire uses open responses for `crt` items.

For scoring responses are labelled as either "Correct", "Intuitive" or "Incorrect". Correct and intuitive answers are as follows:

\`we also code any typos/variations accordingly for all items, see rows 1:3 as illustration)

| Item   | Correct (including variations/typos)        | Intuitive (!!CHECK THESE!!)           |
|---------------|-------------------------------|---------------------------|
| crt_01 | second (or 2nd, 2 or any variation therein) | first (or 1st, 1 or any variation of) |
| crt_02 | 8 (or eight or other variations of/typos)   | 7 (or seven or variations of)         |
| crt_03 | Emily (or typos of)                         | June (or typos)                       |
| crt_04 | 0                                           | 3                                     |
| crt_04 | 5 cents                                     | 10 cents                              |
| crt_05 | 5 minutes                                   | 1 minute                              |
| crt_06 | 47 days                                     | 24 days                               |

### Scoring

The following variables are derived from this measure:

```{r, echo=FALSE, eval=FALSE}
kbl(tstab, booktabs = T) %>%
             kable_styling(full_width = T,
                           fixed_thead = T) %>%
             column_spec(1, width = "3cm") %>%
             column_spec(2, width = "3cm") %>%
             column_spec(3, width = "3cm") %>%
             column_spec(4, width = "3cm") %>%
             column_spec(5, width = "3cm") %>%
             column_spec(6, width = "3cm") 
```
